A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
spellers

We consider only deterministic-action POMDs, where all the uncertainty
in state and action is expressed in the $(\pp{:init})$ declaration. In
sequential sessions, this declaration is used by our approach to
define a starting state, and the set of state-assumptions available to
sequential planning.  Writing \#\ if the value of a proposition is
unspecified, continuing our example from the previous section, we have
the following assumptions:

@@

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term of $(\pp{:init})$. In this
relaxed case, a conjunctive term is visited iff its atomic subterms
are visited, and zero or one of its immediate probabilistic subterms
are visited. For a sequential session, the starting state corresponds
to the unique assumption with probability $1$ -- I.e., the union of
facts from the root conjunctive term. In our example, the starting
state is:

>>>>

We consider only deterministic-action POMDPs, where all state
uncertainty is expressed in the $(\pp{:init})$ declaration. This
declaration is used by our approach to define a starting state, and
the set of state-assumptions available to sequential planning.
Writing \#\ if the value of a proposition is unspecified, continuing
our example from the previous section, we have the following
assumptions:

@@

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term of $(\pp{:init})$. In this
relaxed case, a conjunctive term is visited iff its atomic subterms
are visited, and zero or one of its immediate probabilistic subterms
are visited. For a sequential session, the starting state corresponds
to an assumption (usually unique) with probability $1$. In our
example, the starting state is:
